Removing inclination noise

### 2014-09-15 documents/inclination/inclination.tex
notesToSelf

@@

...Equation dump...
\begin{eqnarray}
Q &\equiv& v\,\sin i
\\
f(Q\given\pars) &=& \int P(Q)\,p(Q\given v,i)\,f(v\given\pars)\,p(i)\,\dd i\,\dd v
\\
\int p(x)\,\dd x &=& 1
\\
\int f(x)\,\dd x &=& E[N]
\\
\ln p(\catalog\given\pars) &=& \sum_{n=1}^N f(Q_n\given\pars) - \ln \int f(Q\given\pars)\,\dd Q
\\
\catalog &\equiv& \setof{Q_n}_{n=1}^N
\\
p(\pars\given\catalog) &=& \frac{1}{Z}\,p(\catalog\given\pars)\,p(\pars)
\\
p(i_n\given\catalog) &=& \int p(i_n\given\pars)\,p(\pars\given\catalog)\,\dd\pars
\\
p(i_n\given\pars) &=& \frac{1}{Z_n}\,\int p(Q_n\given v_n,i_n)\,f(v_n\given\pars)\,p(i_n)\,\dd v_n
\\
p(v_n\given\catalog) &=& \int p(i_n\given\pars)\,p(\pars\given\catalog)\,\dd\pars
\\
p(v_n\given\pars) &=& \frac{1}{Z_n}\,\int p(Q_n\given v_n,i_n)\,f(v_n\given\pars)\,p(i_n)\,\dd i_n
\end{eqnarray}

@@

@@

>>>>

...For specificity we will consider stellar rotation.

@@

...Equation dump...
\begin{eqnarray}
Q &\equiv& v\,\sin i
\\
f(Q\given\pars) &=& \int P(Q)\,p(Q\given v,i)\,f(v\given\pars)\,p(i)\,\dd i\,\dd v
\\
\int p(x)\,\dd x &=& 1
\\
\int f(x)\,\dd x &=& E[N]
\\
\ln p(\catalog\given\pars) &=& \sum_{n=1}^N f(Q_n\given\pars) - \ln \int f(Q\given\pars)\,\dd Q
\\
\catalog &\equiv& \setof{Q_n}_{n=1}^N
\\
p(\pars\given\catalog) &=& \frac{1}{Z}\,p(\catalog\given\pars)\,p(\pars)
\\
p(i_n\given\catalog) &=& \int p(i_n\given\pars)\,p(\pars\given\catalog)\,\dd\pars
\\
p(i_n\given\pars) &=& \frac{1}{Z_n}\,\int p(Q_n\given v_n,i_n)\,f(v_n\given\pars)\,p(i_n)\,\dd v_n
\\
p(v_n\given\catalog) &=& \int p(v_n\given\pars)\,p(\pars\given\catalog)\,\dd\pars
\\
p(v_n\given\pars) &=& \frac{1}{Z_n}\,\int p(Q_n\given v_n,i_n)\,f(v_n\given\pars)\,p(i_n)\,\dd i_n
\end{eqnarray}

@@

...To make an experiment, we need to generate fake data from some true
distribution, and add some noise.
We \emph{also} have to choose a form for the latent distribution
$f(Q\given pars)$; that is, a parameterization $\theta$
Once we have chosen both, we have an experiment.

@@

...Method generalizes to more complex situations; for example when the
censoring depends on variables beyond $Q$, or when the direct
observable is not precisely $Q$ but something intermediate.
